On the Synchronization Power of the Openflow Data Plane

### 2015-04-22 inband-sync.tex
small changes in sec 4

Given our memory interface and using the bundle concept, we can implement
a powerful \emph{Compare-And-Set} (CAS) operation which takes two integer parameters
$\textit{old}$ and $\textit{new}$, reads the register and, if the
value of it is $\textit{old}$, replaces it with $\textit{new}$ and
returns $\top$; otherwise, $\bot$ is returned and
we say that the CAS operation \emph{fails} (which causes an abort of
the invoking transaction). See Algorithm \ref{alg:cas}.

@@

As a second example, let us consider a simple policy update protocol that
allows a set of  controllers to concurrently update switch  \emph{policies}, i.e., sets of
effective flow tables rules, under the
condition that these rules can be composed with the currently installed
policy.
Let us assume that the composition predicate is encoded in a user-specific
$\textit{apply\_update}()$ function~\cite{cpc}.
\liron{TODO: fix the description of the composition predicate - receives a policy and return the commands. we also need to say how a normal controller code can be instrumented to use our paradigm}

Algorithm~\ref{alg:simple-update} is based on the bundle feature and associates each policy with a \emph{policy identifier (pid)}.
In the algorithm, the controller first reads the currently installed
policy and its id \emph{pid}, checks whether the new
policy and the current policy can be composed and, if so, replaces the
current policy with the composition. If, meanwhile, a new
policy (with a different identifier) has been installed, the update
fails and takes no effect.
% \liron{the term composition doesn't make sense now with the new user update function... }

We use increasing numbers as policies
IDs and use them in order to make sure that the new policy, with id
$pid+1$, replaces the (what considered as) current policy, with id
$pid$. Considering the policies IDs, we send the policy installation
commands as part of a bundle that also tries to perform
$CAS(pid,pid+1)$, thereby insuring that the commands are
performed iff the current policy is still there and preventing other
controllers to replace the new policy with another without observing it.

@@

\liron{for alg \ref{alg:simple-update} we should say that switch configuration = \pid + policy}

@@

Algorithm~\ref{alg:update} claims the current policy id in order to prevent someone of using it with different policy in the future (during the current update) and in the bundle used to update the policy it also checks that the new policy id that it about to use (chosen from a finite set of IDs) wasn't claimed by someone else.

@@

\textbf{TODO: fix the pseudocode, make the use of add/delete
  operations uniform, make all switch operations transactional}
  \liron{what does this TODO mean??}

\liron{for alg \ref{alg:update} we should say that switch configuration = \pid + claims + policy}

@@

>>>>

Given our memory interface and using the bundle concept, we can implement
a powerful \emph{Compare-And-Set} (CAS) operation which takes two integer parameters
$\textit{old}$ and $\textit{new}$, reads the register and, if the
value of it is $\textit{old}$, replaces it with $\textit{new}$ and
returns $\top$; otherwise, $\bot$ is returned and
we say that the CAS operation \emph{fails} (which causes an abort of
the invoking transaction). As can be seen Algorithm \ref{alg:cas}, CAS is implemented by two commands. These commands should be sent as part of the same bundle

@@

As a second example, let us consider a simple policy update protocol that
allows a set of  controllers to concurrently update switch  \emph{policies}, i.e., sets of
effective flow tables rules, under the
condition that these rules can be composed with the currently installed
policy.
Let us assume that the composition predicate is encoded in a user-specific
$\textit{apply\_update}()$ function~\cite{cpc}.
Algorithm~\ref{alg:simple-update} uses the bundle feature to update the switch configuration, where the configuration contains both the policy and an abstracted memory address that holds the \emph{policy identifier (pid)} .
In the algorithm, the controller first reads the currently installed
policy and its id \emph{pid}, executes the local update function ($\textit{apply\_update}()$) which results with update commands and then tries to apply them atomically with updating the $pid$. If, meanwhile, a new
policy (with a different identifier) has been installed, the update
fails and takes no effect.
% \liron{the term composition doesn't make sense now with the new user update function... }

\liron{we can explain how a normal controller code can be instrumented to use our paradigm}

We use increasing numbers as policies
IDs and use them in order to make sure that the new policy, with id
$pid+1$, replaces the (what considered as) current policy, with id
$pid$. Considering the policies IDs, we send the policy update
commands as part of a bundle that also tries to perform
$CAS(pid,pid+1)$, thereby insuring that the commands are
performed iff the current policy is still there and preventing other
controllers to replace the new policy with another without observing it.

@@

@@

Algorithm~\ref{alg:update} uses bounded number of policy ids by claiming the current policy id preventing someone of using it with different policy in the future (during the current update) and in the bundle used to update the policy it also checks that the new policy id that it about to use (chosen from a finite set of IDs) wasn't claimed by someone else.

@@

@@

Note that in the case of Algorithm \ref{alg:update}, switch configuration is used to store $pid$ and resource claims (both implemented by flow entries) in addition to the policy.
